Supplementary Information

### 2015-06-29 manuscript/supplement.tex
Double-checked description of rejects in supplement, table is ready except for references
Updated supplemental text.

  To these, we added 7 webs from~\citet{Dunne2013} that were originally used
  to assess the roles of parasites within food webs. As all but 3 of the webs
  from~\citet{GlobalWeb} contained only free-living species, we removed the
  the parasites (and all interactions involving them) from these webs (and the
  3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living
  species only. In addition, we included 30 of the 40 webs
  from~\citet{Riede2011}, which were originally collected to test the
  relationship between consumer and resources body sizes. Nine of the
  remaining webs in the~\citet{Riede2011} dataset were also included in
  the~\citet{GlobalWeb}  dataset, and the last web was derived from an
  unpublished source. This gave us a database of 263 webs. As we wished to use
  the logarithmic form of power-law relationships, we then eliminated any food
  web which did not have at least one each of basal resources, intermediate
  consumers, and top predators (to obtain  non-zero proportions of each
  category). Our final sample size was thereby reduced to XXX food webs.

@@

  \subsubsection*{Results}
    Contrary to the expected latitudinal gradient, the best-fit version of
    equation~(\ref{Latfull}) for species richness did not include a signficant effect of latitude for any ecosystem type except streams
    ($\beta_{Latitude}$=0.095, $p$=0.626; $\beta_{Latitude:Stream}$=-1.69, $p$=0.007).  This
    relationship was robust to the removal of three outliers (based on Cook's Distance). 
    There were also relationships between latitude and link density and between latitude and vulnerability
    in stream food webs, but these trends were non-signficant after the removal of three outliers.
    Link density and vulnerability did not vary with latitude in any other ecosystem type.
    The best-fit version of equation~(\ref{Latfull}) for generality did not include any effect of
    latitude in any ecosystem type.

    The relationships between latitude and the proportions of species at each trophic level were broadly similar
    to the relationship between latitude and species richness. 
    The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.012, $p$\textless0.001) 
    but did not vary with latitude in estuarine, marine, lake, or terrestrial 
    food webs ($\beta_{Latitude}$=0.001, $p$=0.139).
    The proportion of intermediate consumers did not vary with latitude in any ecosystem type.
    The proportion of top predators did not vary with latitude in 
    estuarine, marine, or terrestrial food webs ($\beta_{Latitude}$=0.001, $p$=0.136) but decreased towards the poles in stream and lake food 
    webs ($\beta_{Latitude:Stream}$=-0.006, $p$=0.030; 
    $\beta_{Latitude:Lake}$=-0.006, $p$=0.001). 
    All of these trends were robust to the removal of outliers.

>>>>

  To these, we added 7 webs from~\citet{Dunne2013} that were originally used
  to assess the roles of parasites within food webs. As all but 3 of the webs
  from~\citet{GlobalWeb} contained only free-living species, we removed the
  the parasites (and all interactions involving them) from these webs (and the
  3 webs containing parasites from~\citet{GlobalWeb}) leaving free-living
  species only. In addition, we included 30 of the 40 webs
  from~\citet{Riede2011}, which were originally collected to test the
  relationship between consumer and resources body sizes. Nine of the
  remaining webs in the~\citet{Riede2011} dataset were also included in
  the~\citet{GlobalWeb}  dataset, and the last web was derived from an
  unpublished source. This gave us a database of 263 webs. As we wished to use
  the logarithmic form of power-law relationships, we then eliminated any food
  web which did not have at least one each of basal resources, intermediate
  consumers, and top predators (to obtain  non-zero proportions of each
  category). Our final sample size was thereby reduced to 196 food webs.

@@

  \subsubsection*{Results}
    Contrary to the expected latitudinal gradient, the best-fit version of
    equation~(\ref{Latfull}) for species richness did not 
    include a signficant effect of latitude for any 
    ecosystem type. Further, there were no relationships
    between link density, generality, or vulnerability
    with latitude for any ecosystem type.

    The relationships between latitude and the proportions of species at each trophic level were more complex. 
    The proportion of basal resources increased towards the poles in stream webs ($\beta_{Latitude:Stream}$=0.011, $p$\textless0.001) 
    but did not vary with latitude in estuarine, marine, lake, or terrestrial 
    food webs ($\beta_{Latitude}$=0.001, $p$=0.080),
    while the proportion of intermediate consumers decreased towards the poles in all ecosystem types
    except lakes ($\beta_{Latitude}$=-0.003, $p$=0.015 and
    $\beta_{Latitude:Lake}$=0.005, $p$=0.016).
    The proportion of top predators in a food web, 
    meanwhile, decreased towards the poles in lake and 
    stream food webs but did not vary in other ecosystem
    types ($\beta_{Latitude}$=0.002, $p$=0.151; 
    $\beta_{Latitude:Lake}$=-0.006, $p$=0.001; and
    $\beta_{Latitude:Stream}$=-0.007, $p$=0.006).

    % Does this need to be taken into account? Do I mention
    % it later?
    % All of these trends were robust to the removal of outliers.
    % Was it? Do I even care?
